KidsAIR: Main analysis

### 2020-11-18 main_analysis_final.Rmd
major analysis updates

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 17 Nov 2020"
output: pdf_document
---

@@

# Options for primary model framework

## Poisson model
```{r, echo=TRUE, eval=FALSE}
poisson_results <- glmer(lrti_events_total ~ treatment_assigned + child_age + 
                         (1 | home:cohort:area), 
                         data = analysis_data, family = poisson(link = "log"), 
                         offset = log_person_time_at_risk)
#write_rds(poisson_results, paste0(file_path, "Output/poisson_results.rds"))
```

```{r}
poisson_results <- read_rds(paste0(file_path, "Output/poisson_results.rds"))
summary(poisson_results)
#tidy(poisson_results, conf.int = TRUE)

poisson_simres <- simulateResiduals(poisson_results)
testDispersion(poisson_simres, alternative = "less")
plot(poisson_simres, rank = FALSE, quantreg = TRUE)
```

## Negative binomial model
```{r, echo=TRUE, eval=FALSE}
negbin_results <- glmer.nb(lrti_events_total ~ treatment_assigned + child_age + 
                           (1 | home:cohort:area) + 
                           offset(log_person_time_at_risk), 
                           data = analysis_data)
#write_rds(negbin_results, paste0(file_path, "Output/negbin_results.rds"))
```

```{r}
negbin_results <- read_rds(paste0(file_path, "Output/negbin_results.rds"))
summary(negbin_results)
#tidy(negbin_results, conf.int = TRUE)

negbin_simres <- simulateResiduals(negbin_results)
testDispersion(negbin_simres, alternative = "less")
plot(negbin_simres, rank = FALSE, quantreg = TRUE)
```

## Logistic regression model
```{r, echo=TRUE, eval=FALSE}
logreg_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                        child_age + person_time_at_risk +
                        (1 | home:cohort:area),
                        data = analysis_data, family = binomial, nAGQ = 20)
#write_rds(logreg_results, paste0(file_path, "Output/logreg_results.rds"))
```

```{r}
logreg_results <- read_rds(paste0(file_path, "Output/logreg_results.rds"))
summary(logreg_results)
#tidy(logreg_results, conf.int = TRUE)

logreg_simres <- simulateResiduals(logreg_results)
testDispersion(logreg_simres, alternative = "two.sided")
plot(logreg_simres, rank = FALSE, quantreg = TRUE)
```

```{r}
# Function to clean results
results_function <- function(model_results, model_name) {

@@

# Run results through function, save, combine for plotting
poisson_tidy <- results_function(poisson_results, "Poisson")
negbin_tidy <- results_function(negbin_results, "Neg Bin")
logreg_tidy <- results_function(logreg_results, "Log Reg")

# Combine cleaned results
itt_results_combined <- rbind(poisson_tidy, negbin_tidy, logreg_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("Poisson", "Neg Bin", "Log Reg"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Estimate compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

# Interpretation:
As Jon and I discussed 11/16/20, the Poisson and Negative Binomial models appear to be
underdispersed (variance < mean), not overdispersed (variance > mean). These models 
don't appear to be the best fit for our data. Additionally, results from the models 
were essentially the same.  
The Logistic Regression model appears to be a better fit for the data (no concerns 
in the diagnostic plots). The good news is that the results were also very similar to 
the Poisson/NegBin models, so we don't have to explain any big differences in results 
if model selection concerns come up with reviewers. The bad news is that regardless 
of model, there is no difference in LRTI between treatment arms.   
Given these results, I'm leaning towards using the logistic regression model for the 
primary ITT framework. There are models that can be used for underdispersed count 
data (generalized Poisson regression?), but I can't find a good way to run those 
as mixed models like we need to do. I think the logistic regression model will be 
easier to explain/interpret, and we aren't really losing much information since there 
were so few children with 2+ cases of LRTI.

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 18 Nov 2020"
output: pdf_document
---

@@

# Intent-to-treat framework, LRTI outcome

```{r, echo=TRUE}
# Run primary model and print results
itt_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
#write_rds(itt_results, paste0(file_path, "Output/itt_results.rds"))
```

## Model summary and diagnostic plots
```{r}
summary(itt_results)
itt_res <- simulateResiduals(itt_results)
testDispersion(itt_res, alternative = "two.sided")
plot(itt_res, rank = FALSE, quantreg = TRUE)
```

```{r, eval=FALSE, include=FALSE}
# Run and save model results

itt_winter1_results <- glmer(lrti_events_di_winter ~ treatment_assigned + 
                     child_age + person_time_at_risk_winter +
                     (1 | home:cohort:area),
                     data = analysis_data_winter1, family = binomial, nAGQ = 20)
write_rds(itt_winter1_results, paste0(file_path, "Output/itt_winter1_results.rds"))

itt_winter2_results <- glmer(lrti_events_di_winter ~ treatment_assigned + 
                     child_age + person_time_at_risk_winter +
                     (1 | home:cohort:area),
                     data = analysis_data_winter2, family = binomial, nAGQ = 20)
write_rds(itt_winter2_results, paste0(file_path, "Output/itt_winter2_results.rds"))

itt_income_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + income_3level + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_income_results, paste0(file_path, "Output/itt_income_results.rds"))

itt_filter_type_results <- glmer(lrti_events_di_total ~ treatment_filter_type +  
                     child_age + person_time_at_risk + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_filter_type_results, paste0(file_path, "Output/itt_filter_type_results.rds"))

itt_filter_comp_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + kw_perc_exp_cat2 + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_filter_comp_results, paste0(file_path, "Output/itt_filter_comp_results.rds"))

itt_smoke_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + residents_smoke + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_smoke_results, paste0(file_path, "Output/itt_smoke_results.rds"))

itt_burn_level_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + burn_level_3level + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_burn_level_results, paste0(file_path, "Output/itt_burn_level_results.rds"))

itt_smoking_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_smoking_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_smoking_results, paste0(file_path, "Output/itt_smoking_results.rds"))

itt_windows_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_windows_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_windows_results, paste0(file_path, "Output/itt_windows_results.rds"))

itt_door_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_door_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_door_results, paste0(file_path, "Output/itt_door_results.rds"))

itt_sweep_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + home_act_sweep_sum + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_sweep_results, paste0(file_path, "Output/itt_sweep_results.rds"))

itt_ambpm_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + amb_pm_lrti + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_ambpm_results, paste0(file_path, "Output/itt_ambpm_results.rds"))

itt_ambtemp_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + amb_temp_lrti + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_ambtemp_results, paste0(file_path, "Output/itt_ambtemp_results.rds"))

itt_home_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + 
                     (1 | cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
write_rds(itt_home_results, paste0(file_path, "Output/itt_home_results.rds"))

itt_outlier_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + 
                     (1 | home:cohort:area),
                     data = analysis_data_outliers, family = binomial, nAGQ = 20)
write_rds(itt_outlier_results, paste0(file_path, "Output/itt_outlier_results.rds"))
```

```{r}
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
#itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
#itt_filter_type_results <- read_rds(paste0(file_path, "Output/itt_filter_type_results.rds"))
itt_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_filter_comp_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_ambpm_results <- read_rds(paste0(file_path, "Output/itt_ambpm_results.rds"))
itt_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_ambtemp_results.rds"))
itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

# Function to clean results
results_function <- function(model_results, model_name) {

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
#itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
#itt_filter_type_tidy <- results_function(itt_filter_type_results, "ITT + filt type")
itt_filter_comp_tidy <- results_function(itt_filter_comp_results, "ITT + filt comp")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_ambpm_tidy <- results_function(itt_ambpm_results, "ITT + amb PM")
itt_ambtemp_tidy <- results_function(itt_ambtemp_results, "ITT + amb temp")
itt_home_tidy <- results_function(itt_home_results, "ITT - home")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, 
                              itt_income_tidy, itt_filter_comp_tidy,
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_ambpm_tidy, itt_ambtemp_tidy,
                              itt_home_tidy, itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + filt comp",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp",
                                   "ITT - home", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "LRTI events per child-week \n at risk compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

ITT Winter 1 = Primary model with Winter 1 data only  
ITT + income = Primary model plus categorical income variable  
ITT + filt comp = Primary model plus variable for filter compliance  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period  
ITT - home = Primary model without home as random term  
ITT outlier = Primary model with data that fixes incidence outlier

\pagebreak

# Intent-to-treat framework, PM2.5 outcome

```{r, echo=TRUE}
# Run primary model and print results
itt_pm_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + child_age + 
                       (1 | cohort:area), data = analysis_data_winter1)
#write_rds(itt_pm_results, paste0(file_path, "Output/itt_pm_results.rds"))
```

## Model summary and diagnostic plots
```{r}
summary(itt_pm_results)
plot(itt_pm_results, main = "PM ITT Primary model", 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(itt_pm_results), main = "PM ITT Primary model")
qqline(residuals(itt_pm_results))
```

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try child_age, gender, home_floors_2level, home_sqft_2level

# Run primary model and print results
itt_pm_results_int <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned*home_sqft_2level + 
                              child_age + 
                       (1 | cohort:area), data = analysis_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))

summary(itt_pm_results_int)

int_emtrends <- emtrends(itt_pm_results_int, home_sqft_2level ~ treatment_assigned, var = "log(pm_mean_sampling_period)")
summary(int_emtrends, conf.int = TRUE)
# This line will plot the interaction term
#emmip(itt_pm_results_int, child_age ~ treatment_assigned, cov.reduce = range)
table(model.frame(itt_pm_results_int)$treatment_assigned)
nobs(itt_pm_results_int)
```

```{r, eval=FALSE, include=FALSE}
# Run and save model results

itt_pm_income_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                               child_age + (1 | cohort:area) + 
                               income_3level, data = analysis_data_winter1)
write_rds(itt_pm_income_results, paste0(file_path, "Output/itt_pm_income_results.rds"))

itt_pm_filter_type_results <- glmer(log(pm_mean_sampling_period) ~ treatment_filter_type + 
                                  child_age + (1 | cohort:area), data = analysis_data_winter1)
write_rds(itt_pm_filter_type_results, paste0(file_path, "Output/itt_pm_filter_type_results.rds"))

itt_pm_filter_comp_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                  child_age + (1 | cohort:area) + 
                                  kw_perc_exp_cat2, data = analysis_data_winter1)
write_rds(itt_pm_filter_comp_results, paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))

itt_pm_smoke_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                              child_age + (1 | cohort:area) + 
                              residents_smoke, data = analysis_data_winter1)
write_rds(itt_pm_smoke_results, paste0(file_path, "Output/itt_pm_smoke_results.rds"))

itt_pm_burn_level_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   burn_level_3level, data = analysis_data_winter1)
write_rds(itt_pm_burn_level_results, paste0(file_path, "Output/itt_pm_burn_level_results.rds"))

itt_pm_smoking_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   home_act_smoking_sum, data = analysis_data_winter1)
write_rds(itt_pm_smoking_results, paste0(file_path, "Output/itt_pm_smoking_results.rds"))

itt_pm_windows_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   home_act_windows_sum, data = analysis_data_winter1)
write_rds(itt_pm_windows_results, paste0(file_path, "Output/itt_pm_windows_results.rds"))

itt_pm_door_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   home_act_door_sum, data = analysis_data_winter1)
write_rds(itt_pm_door_results, paste0(file_path, "Output/itt_pm_door_results.rds"))

itt_pm_sweep_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   home_act_sweep_sum, data = analysis_data_winter1)
write_rds(itt_pm_sweep_results, paste0(file_path, "Output/itt_pm_sweep_results.rds"))

itt_pm_ambpm_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   amb_pm_lrti, data = analysis_data_winter1)
write_rds(itt_pm_ambpm_results, paste0(file_path, "Output/itt_pm_ambpm_results.rds"))

itt_pm_ambtemp_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   amb_temp_lrti, data = analysis_data_winter1)
write_rds(itt_pm_ambtemp_results, paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))
```

```{r}
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
itt_pm_filter_type_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_type_results.rds"))
itt_pm_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_ambpm_results <- read_rds(paste0(file_path, "Output/itt_pm_ambpm_results.rds"))
itt_pm_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))

# Run function to clean results
results_function <- function(model_results, model_name) {

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_assigned", "", term),
         model = model_name) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
itt_pm_filter_type_tidy <- results_function(itt_pm_filter_type_results, "ITT filter type")
itt_pm_filter_comp_tidy <- results_function(itt_pm_filter_comp_results, "ITT + filt comp")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_ambpm_tidy <- results_function(itt_pm_ambpm_results, "ITT + amb PM")
itt_pm_ambtemp_tidy <- results_function(itt_pm_ambtemp_results, "ITT + amb temp")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_income_tidy, itt_pm_filter_comp_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_ambpm_tidy, itt_pm_ambtemp_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + filt comp", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "Difference in log(PM2.5) \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

# Save plot as jpg
#ggsave("itt_pm_plot_estimates.jpg", width = 12, height = 6)
```

ITT + income = Primary model plus categorical income variable  
ITT + filt comp = Primary model plus variable for filter compliance  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period

\pagebreak

# Exposure-response framework, LRTI outcome

```{r, echo=TRUE}
# Run primary model and print results
er_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))
```

## Model summary and diagnostic plots
```{r}
summary(er_results)
er_res <- simulateResiduals(er_results)
plot(er_res, rank = TRUE, quantreg = TRUE)
```

```{r, eval=FALSE, include=FALSE}
# Run and save model results

er_income_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_income_results, paste0(file_path, "Output/er_income_results.rds"))

er_filter_comp_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + kw_perc_exp_cat2 +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_filter_comp_results, paste0(file_path, "Output/er_filter_comp_results.rds"))

er_burn_level_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + burn_level_3level +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_burn_level_results, paste0(file_path, "Output/er_burn_level_results.rds"))

er_smoking_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + home_act_smoking_sum +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_smoking_results, paste0(file_path, "Output/er_smoking_results.rds"))

er_windows_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + home_act_windows_sum +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_windows_results, paste0(file_path, "Output/er_windows_results.rds"))

er_door_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + home_act_door_sum +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_door_results, paste0(file_path, "Output/er_door_results.rds"))

er_sweep_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + home_act_sweep_sum +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_sweep_results, paste0(file_path, "Output/er_sweep_results.rds"))

er_ambpm_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + amb_pm_lrti +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_ambpm_results, paste0(file_path, "Output/er_ambpm_results.rds"))

er_ambtemp_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + amb_temp_lrti +
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_ambtemp_results, paste0(file_path, "Output/er_ambtemp_results.rds"))

er_home_results <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + 
                          (1 | cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
write_rds(er_home_results, paste0(file_path, "Output/er_home_results.rds"))
```

```{r}
# Load results
er_results <- read_rds(paste0(file_path, "Output/er_results.rds"))
er_income_results <- read_rds(paste0(file_path, "Output/er_income_results.rds"))
er_filter_comp_results <- read_rds(paste0(file_path, "Output/er_filter_comp_results.rds"))
er_burn_level_results <- read_rds(paste0(file_path, "Output/er_burn_level_results.rds"))
er_smoking_results <- read_rds(paste0(file_path, "Output/er_smoking_results.rds"))
er_windows_results <- read_rds(paste0(file_path, "Output/er_windows_results.rds"))
er_door_results <- read_rds(paste0(file_path, "Output/er_door_results.rds"))
er_sweep_results <- read_rds(paste0(file_path, "Output/er_sweep_results.rds"))
er_ambpm_results <- read_rds(paste0(file_path, "Output/er_ambpm_results.rds"))
er_ambtemp_results <- read_rds(paste0(file_path, "Output/er_ambtemp_results.rds"))
er_home_results <- read_rds(paste0(file_path, "Output/er_home_results.rds"))

# Run function to clean results
results_function <- function(model_results, model_name) {

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("pm_mean", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = "PM2.5",
         model = model_name) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

# Run results through function, save, combine for plotting
er_tidy <- results_function(er_results, "ER Primary")
er_income_tidy <- results_function(er_income_results, "ER + income")
er_filter_comp_tidy <- results_function(er_filter_comp_results, "ER + filt comp")
er_burn_level_tidy <- results_function(er_burn_level_results, "ER + burn level")
er_smoking_tidy <- results_function(er_smoking_results, "ER + smoke act")
er_windows_tidy <- results_function(er_windows_results, "ER + window act")
er_door_tidy <- results_function(er_door_results, "ER + door act")
er_sweep_tidy <- results_function(er_sweep_results, "ER + sweep act")
er_ambpm_tidy <- results_function(er_ambpm_results, "ER + amb PM")
er_ambtemp_tidy <- results_function(er_ambtemp_results, "ER + amb temp")
er_home_tidy <- results_function(er_home_results, "ER - home")

# Combine cleaned results
er_results_combined <- rbind(er_tidy, er_income_tidy, er_filter_comp_tidy, er_burn_level_tidy, 
                              er_smoking_tidy, er_windows_tidy, er_door_tidy,
                              er_sweep_tidy, er_ambpm_tidy, er_ambtemp_tidy, er_home_tidy)
